Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-02-26 index.Rmd
Linebreaks
Added Bibliography

---
title: "Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis."
author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: 
biblio-style: apalike
link-citations: yes
github-repo: OpenPlantPathology/Mungbean_PM
description: "A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew."
---

@@

+ What is the length of a mungbean season and how has it varied in this trial?  
   - This data has not been collected or is not accurate enough to be useful to answer this question.

@@

+ Variability among host genotypes.  
   + The probable influence of season might be influenced by host genotype. This is because newer varieties were adopted into experimental trials as they were released.  
   + Between 2001 and 2015 mungbean genotype changed from Green Diamond, Berken, Crystal to Jade. Jade was the only cultivar used between 2015 and 2019.

>>>>

---
title: "Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis."
author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: "Mungbean.bib"
biblio-style: apalike
link-citations: yes
github-repo: OpenPlantPathology/Mungbean_PM
description: "A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew."
---

@@

+ What is the length of a mungbean season and how has it varied in this trial?

   - This data has not been collected or is not accurate enough to be useful to
   answer this question.

@@

+ Variability among host genotypes.  
   + The probable influence of season might be influenced by host genotype. This
   is because newer varieties were adopted into experimental trials as they were
   released.

   + Between 2001 and 2015 mungbean genotype changed from Green Diamond, Berken,
   Crystal to Jade. Jade was the only cultivar used between 2015 and 2019.
